Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
minor changes

\vincent{Link to \cref{sec:clusterCategories}.}
\vincent{\cref{lem:bijectionMeshMutations} might become a conjecture.}

\begin{lemma}
\label{lem:bijectionMeshMutations}
We have that~$|\principalVariables| = |\meshes| + n$.
\end{lemma}
\begin{proof}
 We postpone the proof until Corollary~\ref{coro::number of positive meshes}.
\end{proof}

The following statement describes the linear dependence in the mesh mutations.

@@

\begin{definition}\label{defn::positive mutation}
Let~$x\in\cluster$ be a cluster variable in a given cluster and let~$x' \in \cluster'$ be obtained by mutating~$\cluster$ at~$x$.
The pair~$(x,x')$ is said to be a \defn{positive mutation} with respect to some initial cluster~$\cluster_\circ$ if there are~$X,Y\in \ind(\cat)$ such that~$\CC(X)=x$,~$\CC(Y)=x'$,~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$ and, for any non-split triangle
\[
X\xrightarrow{} E \xrightarrow{} Y \xrightarrow{h} \susp X 
\]
(this triangle is unique up to isomorphism) we have~$h\in (\susp T)$, where~$T\in\cat$ is any basic cluster-tilting object such that~$\CC(T)=\cluster_\circ$.

@@

\begin{lemma}\label{lemm::exaclty one mesh mutation}
 For every non-initial cluster variable, there exists precisely one pair~$(x,x')$ such that there exists a positive mesh mutation changing~$x$ into~$x'$.
\end{lemma}
\begin{proof}
 Up to isomorphism, there is precisely one almost-split triangle of~$\cat$ starting in~$X$, where~$X$ is the object such that~$\phi(X) = x$.  Thus there is precisely one mesh relation By Lemma~\ref{lemm::almost-split}, the pair~$(x,x')$ is a positive mutation if and only~$X\notin \add(\susp T)$, that is, if and only if~$x$ is not an initial variable.
\end{proof}

\begin{lemma}
\label{lemm::mesh mutations and meshes}
The set of positive mesh mutations~$(x,x')$ of Definition~\ref{defn::positive mutation} is in bijection with the set~$\meshes$ from~\ref{defn::positive mutation}.
\end{lemma}

@@

\begin{corollary}[Lemma~\ref{lem:bijectionMeshMutations}]
\label{coro::number of positive meshes}
 We have that~$|\meshes|$ is the number of non-initial variables.
\end{corollary}
\begin{proof}
 This is a direct consequence of Lemmas~\ref{lemm::exaclty one mesh mutation} and~\ref{lemm::mesh mutations and meshes}.
\end{proof}

>>>>

The following statement is proved in \cref{coro::number of positive meshes}.

\begin{lemma}
\label{lem:bijectionMeshMutations}
We have that~$|\principalVariables| = |\meshes| + n$.
\end{lemma}

The following statement describes the linear dependence in the mesh mutations. It follows from \cref{lem:linearDependencegvectorsCA,def:meshMutation}.

@@

\begin{definition}
\label{defn::positive mutation}
Let~$x\in\cluster$ be a cluster variable in a given cluster and let~$x' \in \cluster'$ be obtained by mutating~$\cluster$ at~$x$.
The pair~$(x,x')$ is said to be a \defn{positive mutation} with respect to some initial cluster~$\cluster_\circ$ if there are~$X,Y\in \ind(\cat)$ such that~$\CC(X)=x$,~$\CC(Y)=x'$,~$\dim_{\field_X}\cat(X, \susp Y) = \dim_{\field_Y}\cat(X, \susp Y) = 1$ and, for any non-split triangle
\[
X\xrightarrow{} E \xrightarrow{} Y \xrightarrow{h} \susp X 
\]
(this triangle is unique up to isomorphism) we have~$h\in (\susp T)$, where~$T\in\cat$ is any basic cluster-tilting object such that~$\CC(T)=\cluster_\circ$.

@@

\begin{lemma}
\label{lemm::exaclty one mesh mutation}
For every non-initial cluster variable, there exists precisely one pair~$(x,x')$ such that there exists a positive mesh mutation changing~$x$ into~$x'$.
\end{lemma}

\begin{proof}
Up to isomorphism, there is precisely one almost-split triangle of~$\cat$ starting in~$X$, where~$X$ is the object such that~$\phi(X) = x$.  Thus there is precisely one mesh relation By \cref{lemm::almost-split}, the pair~$(x,x')$ is a positive mutation if and only~$X\notin \add(\susp T)$, that is, if and only if~$x$ is not an initial variable.
\end{proof}

\begin{lemma}
\label{lemm::mesh mutations and meshes}
The set of positive mesh mutations~$(x,x')$ of \cref{defn::positive mutation} is in bijection with the set~$\meshes$ of~\cref{defn::positive mutation}.
\end{lemma}

@@

\begin{corollary}[\cref{lem:bijectionMeshMutations}]
\label{coro::number of positive meshes}
We have that~$|\meshes|$ is the number of non-initial variables.
\end{corollary}

\begin{proof}
This is a direct consequence of \cref{lemm::exaclty one mesh mutation,lemm::mesh mutations and meshes}.
\end{proof}
